Software Ticket Quality

### 2017-12-05 proposal/mprop.tex
Add paper on software waste

However, having discussed about software and communication waste, what work has been done
around another major software activity, software cost estimation? The paper from 
\citet{grimstad2006framework} tried to show that poor estimation analysis techniques
in software projects will lead to wrong conclusions regarding cost estimation accuracy.
Moreover, they also propose a framework for better analysis of software cost estimation
error. They approached a real-world company where they conducted analysis on their cost
estimation techniques. Eventually, they learned that regular, straight-forward types
of cost estimation analysis techniques errors lead to wrong conclusions, thus increasing
the risk of poor coordination activities.

\textbf{Effects of process maturity on quality, cycle time and effort in software product development}\cite{harter2000effects}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The research tries to investigate the relationship between process maturity, quality, cycle time and effort in software projects. The authors are mainly trying to prove/reject a couple of hypotheses: higher levels of process maturity lead to higher product quality in software projects, higher levels of process maturity are associated with increased cycle time in software products, higher product quality is associated with lower cycle time, higher levels of process maturity lead to increased development efforts in the project and higher product quality is associated with lower development effort.
  \item \textbf{What was the method?}
  In order to test their hypotheses, the authors examined data coming from 30 projects belonging to the systems integration division from a large IT company. The process improvement data was collected via external divisions and by government agencies to provide independent assessments of the firm’s software development processes. Then, they analyzed a couple of key variables and see how they interact: process maturity, product quality, cycle time, development effort, product size, domain/data/decision complexity and requirements ambiguity.
  \item \textbf{What did they learn?}
  They learned that the main features they inspected are additively separable and linear. Moreover, they found out that higher levels of process maturity are associated with significantly higher quality, but also with increased cycle times and development efforts. On the other hand, the reductions in cycle time and effort resulting from improved quality outweigh the marginal increases from achieving more process maturity.
  \item \textbf{Relevance to our work}:
  It can aid our research through better understanding of how various factors can influence the software development processes, thus giving more value to our own research (i.e. being able to automatically determine issue quality could improve better issue writing guidelines/better rules to be enforced, thus reduced triaging and development costs). 
\end{itemize}

>>>>

However, having discussed about software and communication waste, what work has been done
around another major software activity, i.e. software cost estimation? The paper from 
\citet{grimstad2006framework} tried to show that poor estimation analysis techniques
in software projects will lead to wrong conclusions regarding cost estimation accuracy.
Moreover, they also propose a framework for better analysis of software cost estimation
error. They approached a real-world company where they conducted analysis on their cost
estimation techniques. Eventually, they learned that regular, straight-forward types
of cost estimation analysis techniques errors lead to wrong conclusions, thus increasing
the risk of poor coordination activities.

But what happens when a project gains maturity? A work that investigates the effects of process
maturity on quality, cycle time and effort is the one undergone by \citet{harter2000effects}. The
research tries to prove or reject several hypotheses, such as higher levels of process maturity lead 
to higher product quality, higher levels of process maturity are associated with increased cycle time,
higher product quality is associated with lower cycle time, higher levels of process maturity lead 
to increased development efforts in the project and higher product quality is associated with lower
development effort. The authors examined data coming from 30 projects belonging to the systems 
integration division from a large IT company and analyzed a couple of key variables and see how
they interact (i.e. process maturity, product quality, cycle time, development effort, product
size, domain/data/decision complexity and requirements ambiguity). They learned that the main
features they inspected are additively separable and linear. Moreover, they found out that 
higher levels of process maturity are associated with significantly higher quality, but also
with increased cycle times and development efforts. On the other hand, the reductions in cycle
time and effort resulting from improved quality outweigh the marginal increases from achieving
more process maturity.

\textbf{Effects of process maturity on quality, cycle time and effort in software product development}\cite{harter2000effects}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The research tries to investigate the relationship between process maturity, quality, cycle time and effort in software projects. The authors are mainly trying to prove/
  reject a couple of hypotheses: higher levels of process maturity lead to higher product quality in software projects, higher levels of process maturity are associated 
  with increased cycle time in software products, higher product quality is associated with lower cycle time, higher levels of process maturity lead to increased 
  development efforts in the project and higher product quality is associated with lower development effort.
  \item \textbf{What was the method?}
  In order to test their hypotheses, the authors examined data coming from 30 projects belonging to the systems integration division from a large IT company. The process 
  improvement data was collected via external divisions and by government agencies to provide independent assessments of the firm’s software development processes. Then, 
  they analyzed a couple of key variables and see how they interact: process maturity, product quality, cycle time, development effort, product size, domain/data/decision 
  complexity and requirements ambiguity.
  \item \textbf{What did they learn?}
  They learned that the main features they inspected are additively separable and linear. Moreover, they found out that higher levels of process maturity are associated 
  with significantly higher quality, but also with increased cycle times and development efforts. On the other hand, the reductions in cycle time and effort resulting from 
  improved quality outweigh the marginal increases from achieving more process maturity.
  \item \textbf{Relevance to our work}:
  It can aid our research through better understanding of how various factors can influence the software development processes, thus giving more value to our own research 
  (i.e. being able to automatically determine issue quality could improve better issue writing guidelines/better rules to be enforced, thus reduced triaging and 
  development costs). 
\end{itemize}
